\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Page margins
\geometry{margin=1in}

% Custom colors and section styling
\definecolor{primaryblue}{RGB}{31, 73, 125}
\titleformat{\section}{\large\bfseries\color{primaryblue}}{\thesection.}{0.5em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Course Syllabus: Building Quantum Computers}} \\
    \vspace{0.5em}
    {\large \textbf{Master in Quantum Computing}} \\
    \vspace{0.2em}
    {\large \textit{Semester 2}}\\
    \vspace{1em}
    {\large University of Setif 1}
\end{center}

\vspace{1.5em}

\section{Overview of Current Technologies}
\begin{itemize}[noitemsep]
    \item Two-level systems.
    \item Bloch Sphere from an Experimental Point of View.
    \item DiVincenzo's Criteria.
\end{itemize}

\section{Superconducting Qubits}
\begin{itemize}
    \item \textbf{Introduction to Superconductivity:} Cooper Pairs.
    \item \textbf{Josephson Junctions:} Introduction; Quantum tunneling and Josephson Tunneling; Josephson Energy and Washboard Potential; SQUID.
    \item \textbf{Superconducting Qubits:}
    \begin{itemize}[noitemsep]
        \item LC Oscillator, Anharmonic Oscillators and The Josephson Junction.
        \item Cooper Pair Box -- Artificial Atom: Josephson junction as a two-level system.
        \item Transmon qubit: fundamentals (e.g., resonant frequency, anharmonicity).
        \item Circuit QED, Jaynes-Cummings model, Vacuum-Field Rabi Oscillations, Dispersive Model, Qubit Readout.
    \end{itemize}
    \item \textbf{Sources of Decoherence}
    \item \textbf{Other Qubits:} Charge, Phase, and Flux Qubits.
    \item \textbf{Quantum Gates:} Circuit Quantum Electrodynamics (QED), CNOT Gate Using Charge Qubits.
\end{itemize}

\section{Atomic Qubits}
\begin{itemize}[noitemsep]
    \item Relevant Structure of Atoms.
    \item Trapping and Cooling Atoms and Ions.
    \item Ion trap Quantum Gates.
    \item Sources of Decoherence.
\end{itemize}

\section{Spin Qubits}
\begin{itemize}[noitemsep]
    \item Spin in an External Magnetic Field.
    \item Spin Qubits in Silicon.
    \item Spin Qubits in Diamond NV Centers.
    \item Sources of Decoherence.
\end{itemize}

\section{Photonic Qubits}
\begin{itemize}[noitemsep]
    \item Basic Optical Components and Single Photon Sources.
    \item Polarization, Optical Angular Mode Encoded Qubits.
    \item Entangled Photons and Manipulations and Cluster States.
    \item Sources of Decoherence.
\end{itemize}

\vspace{1cm}

\section*{Evaluation}
\begin{itemize}[label=--]
    \item Final exam: 60\%
    \item Personal work: 40\%
\end{itemize}

\end{document}